Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-03-28 latex/comp_or.tex
Paper CompOR update

\subsection{Results before 3D packing}

@@

@@

\begin{table}[H]
	\centering
	\caption{Volume surpluses, methods and scenarios results {\bf before} 3D packing}  \label{tab:results}
	\footnotesize
	%\scriptsize
	\begin{tabular}{crcccccccc}
		\toprule
		{\bf Volume}     &{\bf Resolution}&                              &\multicolumn{6}{c}{\bf Scenarios}                                                   &{\bf Normalized}\\
		\cmidrule{4-9}		
		{\it surplus}    &{\it method}    & {\bf Results}                &{\bf 1}    &{\bf 2}    &{\bf 3}    &{\bf 4}    &{\bf 5}    &{\bf 6}    &{\bf Speedup} \\
		\toprule	
		\multirow{6}{*}{$1.2$}&$Relaxed$  & $f$                &{\it 12.23}&{\it 8.67} &{\it 12.67}&{\it 15.36}&{\it 16.29}&{\it 16.20}&  \specialcell{{\bf 1.00}} \\%  8142
		&                      $MIP$      & {\it run time (s)} &     3     &     13    &     20    &     78   &      198  &     1103  &  1.00 \\% 439							
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &     10.34 &     8.50  &     12.42 &     15.06 &     15.97 &     15.88 &  0.96 \\% 7817
		&                                 & {\it run time (s)} &     < 1   &     3     &     5     &     20    &     58    &     352   &  1.00 \\% 439			
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &   12.96   &   7.53    &  12.28    &   13.20   &  13.71    &   13.44   &  0.90\\% 7278
		&                                 & {\it run time (s)} &     < 1   &     2     &     2     &     8    &     22    &     120   &  {\bf 2.80}\\%
		\midrule		
		\multirow{6}{*}{$1.5$}&$Relaxed$  & $f$                &{\it 17.01}&{\it 12.45}&{\it 18.02}&{\it 22.03}&{\it 23.09}&{\it 22.35}&  \specialcell{{\bf 1.00}} \\%11495  
		&                       $MIP$     & {\it run time (s)} &     6     &     25    &     41    &     158   &      401  &     2161  &  1.00\\%					
        \cmidrule{2-10}		                       
        &\multirow{2}{*}{ $Shims$}        & $f$                &     14.68 &     12.21 &     17.67 &  21.01    &  22.64    &   21.91   &  0.96  \\%  11012
        &                                 & {\it run time (s)} &     < 1   &     2     &     3     &     12    &     33    &   209     &  1.00 \\% 260
        \cmidrule{2-10}		                      
        &\multirow{2}{*}{ $mpShims$}      & $f$                &    16.12  &     11.81 &     17.48 &  17.66    &   19.81   &  17.61    &  0.87 \\% 9966
        &                                 & {\it run time (s)} &     < 1   &     1     &     2     &     7     &   20      &  120      &  {\bf 1.70}\\% 151
		\midrule
		\multirow{6}{*}{$2.0$}&$Relaxed$  & $f$                &{\it 24.56}&{\it 17.47}&{\it 25.19}&{\it 27.94}&{\it 29.90}&{\it 27.60 }&  \specialcell{{\bf 1.00}} \\%15266  
		&                       $MIP$     & {\it run time (s)} &     6     &     25    &     41    &     158   &      401  &     2161  & 1.00\\%							
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &    21.31  &  17.35    &   24.24   &   27.39    &  29.31     &  27.06     &   0.96  \\%  14666
		&                                 & {\it run time (s)} &     < 1   &     2     &     4     &     14     &     35     &   220     &  1.00 \\% 260
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &    24.33  &   17.26   &   24.70   &  24.81     &   27.71    &  24.93        &  0.94  \\% 14374
		&                                 & {\it run time (s)} &     < 1   &     2     &     3     &     9      &   26       &  151      &  {\bf 1.70}\\% 151
		\bottomrule	
	\end{tabular}
	\normalsize
\end{table}

@@

\subsection{Results after 3D packing}

\vspace{2.0mm}
\begin{table}[H]
	\centering
\color{blue}{	
	\caption{Volume surpluses, methods and scenarios results {\bf after} 3D packing}  \label{tab:results2}
}
	\footnotesize
	\begin{tabular}{crcccccccc}
		\toprule
		{\bf Volume}     &{\bf Resolution}&                    &\multicolumn{6}{c}{\bf Scenarios}                                                   &{\bf Normalized}\\
		\cmidrule{4-9}		
		{\it surplus}    &{\it method}    & {\bf Results}      &{\bf 1}    &{\bf 2}    &{\bf 3}    &{\bf 4}    &{\bf 5}    &{\bf 6}    &{\bf Speedup} \\
		\toprule
		\multirow{6}{*}{$1.2$}&$Relaxed$  & $f$                &{\it 11.47}&{\it 7.24} &{\it 10.78}&{\it 12.06}&{\it 12.97}&{\it 12.44}&  \specialcell{{\bf 1.00}} \\%
		&                       $MIP$     & {\it run time (s)} &     6     &     25    &     41    &     158   &      401  &     2161  &  1.00\\%					
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &    9.05   &   5.11    &   9.75    &   10.96   &   12.86   &   13.25   &  0.96 \\% 7817
		&                                 & {\it run time (s)} &     16    &     68    &     94    &    323    &    719    &    3549   &  1.00 \\% 439			
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &    12.14  &   7.29    &   10.36   &   12.63   &   14.04   &   13.92   &  0.90\\% 7278
		&                                 & {\it run time (s)} &     9     &     36    &     54    &     192   &     427   &    2118   &  {\bf 2.80}\\%		
		\midrule		
		\multirow{6}{*}{$1.5$}&$Relaxed$  & $f$                &{\it 15.83}&{\it 10.08}&{\it 15.14}&{\it 16.87}&{\it }&{\it }&  \specialcell{{\bf 1.00}} \\%11495  
		&                      $MIP$      & {\it run time (s)} &    10     &     43    &     72    &     262   &     58    &     352   &  1.00 \\% 439					
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &   11.55   &   7.61   &   12.28   &   15.00   &   17.55   &   17.57   &  0.96  \\%  11012
		&                                 & {\it run time (s)} &    25     &    107   &     156   &    498    &    1217   &   5743     &  1.00 \\% 260
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &   17.05   &   10.01   &   15.01  &   16.75   &   20.09   &      &  0.87 \\% 9966
		&                                 & {\it run time (s)} &    18     &    64     &     101  &    351    &   828     &  120      &  {\bf 1.70}\\% 151
		\midrule
		\multirow{6}{*}{$2.0$}&$Relaxed$  & $f$                &{\it 23.73}&{\it }&{\it }&{\it }&{\it }&{\it  }&  \specialcell{{\bf 1.00}} \\%15266  
		&                       $MIP$     & {\it run time (s)} &    14     &     3     &     5     &     20    &     58    &     352   &  1.00 \\% 439					
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &   16.28   &      &      &       &       &       &   0.96  \\%  14666
		&                                 & {\it run time (s)} &    37     &     2     &     4     &     14     &     35     &   220     &  1.00 \\% 260
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &   24.52   &      &      &       &       &          &  0.94  \\% 14374
		&                                 & {\it run time (s)} &    27     &     2     &     3     &     9      &   26       &  151      &  {\bf 1.70}\\% 151
		\bottomrule	
	\end{tabular}
	\normalsize
\end{table}

@@

(3) The procedure for 3-D packing generated an unfit item percentage of approximately 17\%, in average. 
We are conscious that this unfit rate could be smaller if we had chosen \cite{PaquayLimbourgSchynsOliveira2018} approaches, but as we are concerned with an operational application where the running time is crucial, we stick to an approximate approach.

@@

This solution phase was a parallel 3-D packing with each pallet as a process, which decreased this phase's run time by approximate a $n-1$ factor where $n$ is the number of processes. This was possible because each packing process is completely independent; there is no multiprocessing shared memory. It is also important to highlight that, after the items were excluded, the CG deviation was kept within its operational and feasible range.

@@

>>>>

\subsection{Results {\bf before} 3D packing}

@@

Note that, in Table \ref{tab:results} all $Relaxed\ MIP\ f$ value are italicized to indicate that these values may not be optimal or feasible as the decision variables are not integers.

@@

\begin{table}[H]
	\centering
	\caption{Volume surpluses, methods and scenarios results {\bf before} 3D packing}  \label{tab:results}
	\footnotesize
	%\scriptsize
	\begin{tabular}{crcccccccc}
		\toprule
		{\bf Volume}     &{\bf Resolution}&                              &\multicolumn{6}{c}{\bf Scenarios}                                                   &{\bf Normalized}\\
		\cmidrule{4-9}		
		{\it surplus}    &{\it method}    & {\bf Results}      &{\bf 1}    &{\bf 2}    &{\bf 3}    &{\bf 4}    &{\bf 5}    &{\bf 6}    &{\bf Speedup} \\
		\toprule	
		\multirow{7}{*}{$1.2$}&$Relaxed$  & $f$                &{\it 12.23}&{\it 8.67} &{\it 12.67}&{\it 15.36}&{\it 16.29}&{\it 16.20}& - \\%  
		&                      $MIP$      & {\it run time (s)} &     3     &     13    &     20    &     78    &      198  &     1103  & - \\% 							
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &     10.34 &{\bf 8.50} &{\bf 12.42}&{\bf 15.06}&{\bf 15.97}&{\bf 15.88}&{\bf 0.97} \\%   best 8079
		&                                 & {\it run time (s)} &     < 1   &     3     &     5     &     20    &     58    &     352   &  1.00 \\% 	439		
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &{\bf 12.96}&   7.53    &  12.28    &   13.20   &  13.71    &   13.44   &  0.91\\% 
		&                                 & {\it run time (s)} &     < 1   &     2     &     2     &     8     &     22    &     120   &  {\bf 2.80}\\% 155
		\toprule		
		\multirow{7}{*}{$1.5$}&$Relaxed$  & $f$                &{\it 17.01}&{\it 12.45}&{\it 18.02}&{\it 22.03}&{\it 23.09}&{\it 22.35}& - \\%  
		&                       $MIP$     & {\it run time (s)} &     4     &     20    &     32    &     115   &     296   &     1685  &  -\\%					
        \cmidrule{2-10}		                       
        &\multirow{2}{*}{ $Shims$}        & $f$                &     14.68 &{\bf 12.21}&{\bf 17.67}&{\bf 21.01}&{\bf 22.64}&{\bf 21.91}&{\bf 0.99}  \\%  best 11156
        &                                 & {\it run time (s)} &     < 1   &     2     &     3     &     12    &     33    &   209     &  1.00 \\% 
        \cmidrule{2-10}		                      
        &\multirow{2}{*}{ $mpShims$}      & $f$                &{\bf 16.12}&     11.81 &     17.48 &  17.66    &   19.81   &  17.61    &  0.90 \\% 
        &                                 & {\it run time (s)} &     < 1   &     1     &     2     &     7     &   20      &  120      &  {\bf 1.70}\\% 
		\toprule
		\multirow{7}{*}{$2.0$}&$Relaxed$  & $f$                &{\it 24.56}&{\it 17.47}&{\it 25.19}&{\it 27.94}&{\it 29.90}&{\it 27.60}& -\\%  
		&                       $MIP$     & {\it run time (s)} &     4     &     23    &    34     &   119     &     317      &           & -\\%							
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &    21.31  &{\bf 17.35}&   24.24   &{\bf 27.39}&{\bf 29.31}&{\bf 27.06}&{\bf 0.98}  \\%  best 15014
		&                                 & {\it run time (s)} &     < 1   &     2     &     4     &     14    &     35    &   220     &  1.00 \\% 
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &{\bf 24.33}&   17.26   &{\bf 24.70}&   24.81   &   27.71   &  24.93    &  0.96  \\% 
		&                                 & {\it run time (s)} &     < 1   &     2     &     3     &     9     &   26      &  151      &  {\bf 1.70}\\% 
		\bottomrule	
	\end{tabular}
	\normalsize
\end{table}

@@

\subsection{Results {\bf after} 3D packing}

Although the relaxed MIP solver results are not always feasible, the multiprocessing 3D packing turns them feasible regarding dimensions and weight. So, in Table \ref{tab:results2}, we considered it's results in the performance comparisons.

\vspace{2.0mm}
\begin{table}[H]
	\centering
\color{blue}{	
	\caption{Volume surpluses, methods and scenarios results {\bf after} 3D packing}  \label{tab:results2}
}
	\footnotesize
	\begin{tabular}{crcccccccc}
		\toprule
		{\bf Volume}     &{\bf Resolution}&                    &\multicolumn{6}{c}{\bf Scenarios}                                                   &{\bf Normalized}\\
		\cmidrule{4-9}		
		{\it surplus}    &{\it method}    & {\bf Results}      &{\bf 1}    &{\bf 2}    &{\bf 3}    &{\bf 4}    &{\bf 5}    &{\bf 6}    &{\bf Speedup} \\
		\toprule
		\multirow{7}{*}{$1.2$}&$Relaxed$  & $f$                &   11.47   &    7.24   &{\bf 10.78}&     12.06 &     12.97 &    12.44  &     0.95 \\%
		&                       $MIP$     & {\it run time (s)} &     6     &     25    &     41    &     158   &      401  &     2161  &{\bf 1.70}\\% 2792					
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &    9.05   &   5.11    &   9.75    &   10.96   &   12.86   &   13.25   &     0.86 \\% 
		&                                 & {\it run time (s)} &     16    &     68    &     94    &    323    &    719    &    3549   &     1.00 \\% 	4769		
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &{\bf 12.14}&{\bf 7.29} &   10.36   &{\bf 12.63}&{\bf 14.04}&{\bf 13.92}&{\bf 0.99}\\% best 7080
		&                                 & {\it run time (s)} &     9     &     36    &     54    &     192   &     427   &    2118   &{\bf 1.70}\\%	2836	
		\toprule		
		\multirow{7}{*}{$1.5$}&$Relaxed$  & $f$                &     15.83 &{\bf 10.08}&{\bf 15.14}&{\bf 16.87}&     18.58 &     17.52 &     0.97 \\%  
		&                      $MIP$      & {\it run time (s)} &    10     &     43    &     72    &     262   &     696   &     3741  &{\bf 1.60} \\% 4824					
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &   11.55   &   7.61    &   12.28   &   15.00   &   17.55   &   17.57   &  0.84  \\%  
		&                                 & {\it run time (s)} &    25     &    107    &     156   &    498    &    1217   &   5743    &  1.00 \\% 7746
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &{\bf 17.05}&   10.01   &   15.01   &   16.75   &{\bf 20.09}&{\bf 17.85}&{\bf 1.00} \\%   best 9708
		&                                 & {\it run time (s)} &    18     &    64     &     101   &    351    &   828     &  3879     &     1.50\\% 5421
		\toprule
		\multirow{7}{*}{$2.0$}&$Relaxed$  & $f$                &     23.73 &{\bf 15.23}&   21.96   &   24.22   &   26.69   &           &  {\bf 1.00} \\%  
		&                       $MIP$     & {\it run time (s)} &    14     &     59    &     95    &    348    &   880     &         &  1.00 \\% 					
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &   16.28   &   10.93   &   18.16   &   22.35   &   25.12   &   24.53    &   0.96  \\%  
		&                                 & {\it run time (s)} &    37     &    141    &   196     &     653   &   1453    &   6851     &  1.00 \\% 
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &{\bf 24.52}&   15.18   &{\bf 21.99}&{\bf 24.61}&{\bf 26.94}&   24.83    &  0.94  \\% 
		&                                 & {\it run time (s)} &    27     &    87     &   146     &    496    &   1080    &   5160     &  {\bf 1.70}\\% 
		\bottomrule	
	\end{tabular}
	\normalsize
\end{table}

@@

(3) The procedure for 3-D packing generated an unfit item rate of, on average, 17\% after {\it Shims} solutions, 13\% after {\it mpShims} solutions, and 9\% after the MIP solver solutions. 
We are conscious that this unfit rate could be smaller if we had chosen \cite{PaquayLimbourgSchynsOliveira2018} approach, but as we are concerned with an operational application where the running time is crucial, we stick to faster approximate approaches like the {\it First Fit Decreasing} (first orientation that fits) and the {\it Best Fit} (best pivot point if more than one is available).

@@

This solution phase was a multiprocessing 3-D packing with each pallet as a process, which decreased this phase's run time by approximate a $n-1$ factor where $n$ is the number of processes. This was possible because each packing process is completely independent; there is no multiprocessing shared memory. It is also important to highlight that, after the items were excluded, the CG deviation was kept within its operational and feasible range.

@@

Another important discovery is that the relaxed version of the MIP solver followed by the multiprocessing 3D packing yielded efficient solutions, even a little bit faster than {\it mpShims} (Table \ref{tab:results2}), but not surpassing {\it mpShims}' quality results.
